Dark matter halo shape at $z=0$ in the Auriga simulations: radial evolution and alignment with the stellar disk

### 2019-07-19 Document/paper.tex
intro

Accurate observations and modeling of our Galaxy 
shape our understanding of the Universe as a whole.  
Explaining the Galaxy's matter composition and kinematical state is 
equivalent to figuring out its formation process in a cosmological
context. 
As a first approximation, the Milky Way's (MW) morphology and
separation into global kinematically coherent components, such as its
disk and bulge, can be used to support the  existence of a Dark Matter
(DM) component to explain its dynamics around the solar neighborhood
\citep{2000MNRAS.311..361O,2009PASJ...61..227S,2010JCAP...08..004C,2013ApJ...779..115B,Iocco15}.

>>>>

The understanding of our Universe as a whole is greatly influenced by
accurate observations and modeling of our Galaxy 
Explaining the Galaxy's matter composition and kinematical state is 
equivalent to figuring out its formation process in a cosmological
context. 
As a first approximation, the Milky Way's (MW) morphology and
separation into global kinematically coherent components, such as its
disk and bulge, can be used to support the  existence of a Dark Matter
(DM) component to explain its dynamics around the solar neighborhood
\citep{2000MNRAS.311..361O,2009PASJ...61..227S,2010JCAP...08..004C,2013ApJ...779..115B,Iocco15}.
